\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=2cm}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{enumitem}
\usepackage{qrcode}
\usepackage{hyperref}

% ---- Style tweaks ----
\pagenumbering{gobble}
\definecolor{primary}{HTML}{003366}
\hypersetup{
  colorlinks=true,
  urlcolor=primary,
  linkcolor=primary
}

\begin{document}

\newcommand{\cvsection}[1]{%
    \section*{%
        #1\hspace{0.5em}%
        \leaders\hbox{\rule[0.5ex]{1pt}{0.4pt}}\hfill\kern0pt%
    }%
}


\newcommand{\FirstName}{Roque}
\newcommand{\MiddleName}{Ivan}
\newcommand{\LastName}{Lopez}

% ---- Header ----
\begin{center}
    {\Huge \bfseries \MakeUppercase {Roque Ivan Lopez}} \\[10pt]
    {\Large Project Manager \& AI Implementation Specialist} \\[6pt]    
    \faEnvelope\ Email: \href{mailto:roqueilopez@gmail.com}{roqueilopez@gmail.com} $|$ 
    \faPhone\ Mobile: \href{https://wa.me/message/UDT3S3HIATXDM1}{+353 (083) 079 9336} $|$ 
    \faMapPin\ Location: \href{https://share.google/zzGhtrte6JsxdfIUU}{Dublin, Ireland} \\
    
    \faLinkedin\ LinkedIn: \href{https://www.linkedin.com/in/roqueilopez}{linkedin.com/in/roqueilopez} $|$ 
    \faGithub\ GitHub: \href{https://github.com/Ruxterlo}{github.com/Ruxterlo} \\
    \faGlobe\ AI-Interactive CV Website: \href{https://mi-cv-dinamico.com} {  \qrcode[height=1cm]{https://mi-cv-dinamico.com}} \faMousePointer

\end{center}

\vspace{0.4cm}

\textbf{Availability \& Visa Information:} 1G Visa; Eligible to work full-time in Ireland with no restrictions. Notice period: two weeks.

% ---- Professional Summary ----
\cvsection{Professional Summary}
Innovative professional with a Master’s in AI and  experience as a Software Architect, Key Account Manager, and System Implementer. Experienced in teaching, with a client-centric approach and a proven ability to deliver impactful solutions that enhance processes, transparency, and business growth. Recognized as a top-performing implementer, receiving both client commendations and company recognitions for successful system deliveries and rollouts. Led implementations for major franchises in Mexico, ensuring smooth rollouts that allowed staff to operate new systems from day one without disrupting business operations. Reduced database architecture timelines from four weeks to just one, accelerating system delivery and increasing client satisfaction. Skilled at designing and conducting formal training for franchise owners and employees, providing ongoing operational support, which strengthened client trust and secured contracts with at least four leading franchises. Streamlined client management by combining issue resolution and relationship building into a single role that previously required two full-time positions, eliminating inefficiencies and optimizing workload distribution. 

% ---- Technology Skills ----
\cvsection{Technology Skills}
\setlength{\itemsep}{-5pt}
\begin{itemize}[leftmargin=1.2em]
    \item \textbf{SQL Management:} MySQL, PostgreSQL, SQL Server; queries, triggers, routines.
    \item \textbf{Python:} Data analysis, web scraping, automation, API development, and other libraries.
    \item \textbf{Business Intelligence (BI):} Dashboards, reports, data modelling, DAX queries with Power BI.
    \item \textbf{Virtualization:} Server setup, configuration, troubleshooting. Proficient in VMware, Hyper-V.
    \item \textbf{Artificial Intelligence:} ML, NN, DL, CV, NLP, TSF, LLMs, Chatbots, Face Recognition.
\end{itemize}

\textbf{Certifications:} TestOut PC Pro, TestOut Hybrid Server Pro: Core, TestOut Client Pro.

% ---- Education ----
\cvsection{Education}
\textbf{2024-2025} $|$ National College of Ireland $|$ MSc in Artificial Intelligence for Business $|$ Dublin, Ireland

\textbf{Key Modules:} AI \& Data Management, AI Strategy \& Implementation, Risk \& Sustainability.

    
\vspace{0.2cm}
\textbf{2024-2027} $|$ Ensign College $|$ BAS Information Technologies $|$ Utah, USA

\textbf{Key Modules:} Python, Cloud Computing, Networks, Databases, Linux, Cybersecurity.


\vspace{0.2cm}
\textbf{2024-2025} $|$ Ensign College $|$ Technical Support Engineer $|$ Utah, USA

\textbf{Key Modules:} IT Support, Networks, Cloud Computing, Python Scripting.

\vspace{0.2cm}
\textbf{2011-2014} $|$ AS Media Vocational Training Center $|$ BA in Business Image Consulting  $|$ Puebla, MX

\textbf{Key Modules:} Communication, Project Management, Marketing, Psychology, Professional Protocol.

% ---- Work Experience ----
\cvsection{Work Experience}

\textbf{09/2022 -- Present} $|$ Gauchos Dog Restaurant $|$ Kitchen Worker $|$ Dublin, Ireland
\begin{itemize}
\setlength{\itemsep}{-5pt}
    \item Implemented an automated inventory system that tracked stock, generated requisitions, and minimized shortages and unnecessary purchases, reducing lost sales due to stockouts by 60\%.
    \item Redesigned restaurant networks infrastructure to resolve instability, ensuring stable connections for all systems.
    \item Developed a customer Wi-Fi portal that preserved company network performance and cut internet expenses by 50\%.
\end{itemize}

\textbf{01/2020 -- 07/2021} $|$ Grupo Telnet  $|$ Key Account Manager $|$ Puebla, MX
\begin{itemize}
\setlength{\itemsep}{-5pt}
    \item Promoted from System Implementer due to efficient rollouts with zero reported issues.
    \item Coordinated system enhancements with the development team, including prototypes and cost/time estimates, improving development efficiency and speed by 80\%.
    \item Closed major franchise deals in Mexico and internationally, boosting client system usage from 30\% to 90\%, restoring on-time payments and loyalty.
\end{itemize}

\textbf{01/2018 -- 12/2020} $|$ Grupo Telnet $|$ Software Architect/Implementer  $|$ Puebla, MX

\begin{itemize}
\setlength{\itemsep}{-5pt}
    \item Led the creation of a dedicated Implementation Department, increasing operational efficiency by 40\% and enabling the company to handle 3x more client implementations.
    \item Designed and implemented standardized rollout processes, halving database setup time from four weeks to two.
    \item Coordinated onboarding for new implementers, using KPIs and assessments to cut errors by 80\% and ensure successful rollouts.
\end{itemize}

% ---- Recent Projects ----
\cvsection{Recent Projects}
\begin{itemize}[leftmargin=1.2em]
\setlength{\itemsep}{-5pt}
  \item \textbf{HR \& Performance Prediction} -- Designed clustering models (K-Means) to match candidates with job postings and propose employee performance evaluation frameworks.
  
  \item \textbf{Financial Forecasting} -- Developed predictive models to analyze stock market trends and generate buy/sell recommendations.
  
  \item \textbf{Enhanced Facial Recognition} -- Proposed an acoustic signature model using reflected echoes and Transformer networks to improve recognition accuracy in low-light conditions.
  
  \item \textbf{Recommendation Systems} -- Built personalized recommendation engines for streaming platforms and food services, integrating user preferences, popularity trends, and budget constraints.
  
  \item \textbf{Multilingual University Chatbot} -- Delivered a functional chatbot prototype enabling students to schedule exams, access FAQs, and check class calendars via text or voice in different languages.\\
\end{itemize}

\begin{multicols}{2}
\cvsection{Languages}

\begin{itemize} [leftmargin=1.2em]
\setlength{\itemsep}{-5pt}
    \item \makebox[2.3cm][l]{\textbf{Spanish:}} {Native}
    \item \makebox[2.3cm][l]{\textbf{English:}} {Fluent (C2)} 
    \item \makebox[2.3cm][l]{\textbf{Portuguese:}} {Intermediate (B1)}
    \item \makebox[2.3cm][l]{\textbf{Italian:}} {Basic (A2)}
    \item \makebox[2.3cm][l]{\textbf{French:}}  {Basic (A2)}

\end{itemize}

\columnbreak

\cvsection{Flexibility \& Mobility}
\begin{itemize}[leftmargin=0.2em]
\setlength{\itemsep}{0pt}
    \item \faIcon{briefcase} \textbf{Travel:} Open to travel \& available to relocate.
    \item \faIcon{users} \textbf{Collaboration:} Effective in cross-cultural and multidisciplinary teams.
    \item \faIcon{laptop} \textbf{On-site/Hybrid/Remote:} Comfortable and productive in any working environment.
\end{itemize}
\end{multicols}

% Sección solo para el outline
\cvsection{Hobbies \& Interests}
Lifelong learning \& reading, outdoor adventures (hiking \& swimming), travel, tech \& innovation, languages, networking \& investing, and volunteering (youth camps, church service, workshops).

\end{document}
